### 2016-01-17 01-intro.tex
Some of Henri's comments got lost

One such big data problem is analyzing large graphs such as social networks where it is not unusual to see a network consisting of billions of edges and tens of million of vertices~\cite{yang2015defining}. In particular, we are interested in the overlapping community detection problem~\cite{xie2013overlapping}, where the goal is to learn the probability distribution of each vertex to participate in each community, provided a set of vertices, the links between them (which are usually very sparse), and the number of latent communities. A community can be seen as a densely connected group of vertices that are only sparsely connect to the rest of the network.

@@

There have been two main recent advances in this direction of scalable Bayesian inference: methods based on stochastic variational Bayes (SVB)~\cite{hoffman2013stochastic,gopalan2013efficient,gopalan2012scalable} and stochastic gradient Markov chain Monte Carlo (SG-MCMC)~\cite{welling2011bayesian,patterson2013stochastic,ahn2014distributed,ahn2012bayesian}. Both methods have the important property that they only require a small subset of the data for every iteration. In other words, they can be applied to (infinite) streaming data.

>>>>

One such big data problem is analyzing large graphs such as social networks where it is not unusual to see a network consisting of billions of edges and tens of million of vertices~\cite{yang2015defining}. In particular, we are interested in the overlapping community detection problem~\cite{xie2013overlapping}, where the goal is to learn the probability distribution of each vertex to participate in each community, given a set of vertices, the links between them (which are usually very sparse), and the number of latent communities. A community can be seen as a densely connected group of vertices that are only sparsely connected to the rest of the network.

@@

There have been two main recent advances in this direction of scalable Bayesian inference: methods based on stochastic variational Bayes (SVB)~\cite{gopalan2012scalable,hoffman2013stochastic,gopalan2013efficient} and stochastic gradient Markov chain Monte Carlo (SG-MCMC)~\cite{welling2011bayesian,patterson2013stochastic,ahn2014distributed,ahn2012bayesian}. Both methods have the important property that they only require a small subset of the data for every iteration. In other words, they can be applied to (infinite) streaming data.
